Particle Interception as a Function of Reynolds Number and Collector Density

### 2021-03-13 code/analysis.Rmd
fixed minus signs in some plots

library(tidyverse)
library(broom)
library(cowplot)
library(lme4)

@@

p1 <- residplot(resids_exp, title = "Exponential Model")
p2 <- residplot(resids_lin, title = "Linear Model")
p3 <- varplot(resids_exp)
p4 <- varplot(resids_lin)

@@

```{r message=FALSE, warning=FALSE, eval = FALSE}

@@

```{r message=FALSE, warning=FALSE, eval = FALSE}

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
  ylab(expression(beta[log(Re[c])]))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(paste("Collector Reynolds Number (",Re[c]," )"))) +
  ylab(expression(beta[log(phi[c])]))

>>>>

library(tidyverse)
library(broom)
library(cowplot)
library(lme4)
library(signs)

@@

p1 <- residplot(resids_exp, title = "Exponential Model") +
  scale_y_continuous(labels = signs_format())
p2 <- residplot(resids_lin, title = "Linear Model")+
  scale_y_continuous(labels = signs_format(accuracy = .1))
p3 <- varplot(resids_exp)
p4 <- varplot(resids_lin)

@@

```{r message=FALSE, warning=FALSE}

@@

```{r message=FALSE, warning=FALSE}

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
  xlab(expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
  ylab(expression(beta[log(Re[c])])) +
  scale_y_continuous(labels = signs_format(accuracy = 1), limits = c(-3,1.5))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
  xlab(expression(paste("Collector Reynolds Number (",Re[c]," )"))) +
  ylab(expression(beta[log(phi[c])])) +
  scale_y_continuous(labels = signs_format(accuracy = 1), limits = c(-3,1.5))
